Sumbission Steps

### 2020-09-29 code/03-submission-steps.Rmd
changed file paths

    ```{r}
    # Individual files to delete
    file.remove("../data/bullet-explain.rds")
    file.remove("../data/bullet-lime.rds")
    file.remove("../data/bullet-rf.rds")
    file.remove("../data/bullet-test.csv")
    file.remove("../data/bullet-test.csv.zip")
    file.remove("../data/bullet-train.csv")
    file.remove("../data/bullet-train.csv.zip")
    file.remove("../data/example-signatures.csv")
    file.remove("../data/example-signatures.csv.zip")
    file.remove("../data/sine-lime-explain.rds")
    file.remove("../figure-static/figure-08-1.eps")
    file.remove("../figure-static/figure-08-1.png.zip")
    file.remove("../figure-static/figure-10-1.eps")
    file.remove("../figure-static/figure-10-1.png")

>>>>

    ```{r}
    # Individual files to delete
    file.remove("../data/bullet-explain.rds")
    file.remove("../data/bullet-lime.rds")
    file.remove("../data/bullet-rf.rds")
    file.remove("../data/bullet-test.csv")
    file.remove("../data/bullet-test.csv.zip")
    file.remove("../data/bullet-train.csv")
    file.remove("../data/bullet-train.csv.zip")
    file.remove("../data/example-signatures.csv")
    file.remove("../data/example-signatures.csv.zip")
    file.remove("../data/sine-lime-explain.rds")
    file.remove("../data/raw/h224-set1-features.rds")
    file.remove("../data/raw/h224-set11-features.rds")
    file.remove("../data/raw/CCFs_withlands.csv")
    file.remove("../data/raw/signatures.rds")
    file.remove("../figure-static/figure-08-1.eps")
    file.remove("../figure-static/figure-08-1.png.zip")
    file.remove("../figure-static/figure-10-1.eps")
    file.remove("../figure-static/figure-10-1.png")
